ClaTex: LaTeX as a Service on the Cloud

### 2017-04-20 paper.tex
windows update

In virtualization environment, guest OS is transparent to the underlying hypervisor. There are only some basic monitoring statics exposed to hypervisor such as VSZ and RSS in linux system. VSZ and RSS are coarse-grained statics which did not reflect the memory usage in a certern period. In the past, working set theory\cite{wss} has been widely used to capture applications' memory needs. Working sets is defined as the set of all pages accessed by a process over a given epoch. However, working set doesn't relate directly to the performance of an application. For example, if an application scans 100 pages sequentially. In a short period, the working set is 100 pages. But allocating 1 page or 100 pages gives the same memory hit ratio because the miss ratio is always 100\%. MRC is the alternative to working set theory. It plots the miss rate against given physical memory. MRC may differ every second reflecting the memory requirement changes of the application which gives us a hint to dynamic allocate more or reclaim spare memory in order to utilize the host machine's resources better.

MRC theroy is a general method to curve the miss rate and each part of the memory hierachy in computer storage including cache, memory and etc. Recently many research focus on the cache MRC construction. Centaur\cite{Koller2015Centaur} implements host-side SSD cache partition for VMs that provides both lower cache miss rate and better performance isolation and performance control for VM workloads. Like Centaur, Multi-Cache\cite{Rajasekaran2016Multi} presents multiple cache management on a set of storage devices and intelligently manages how caches are shared by competing VMs. Moirai\cite{Stefanovici2015Software} presents a tenant- and workload-aware system that allows data center providers to control their distributed caching infrastructure.

>>>>

In virtualization environment, guest OS is transparent to the underlying hypervisor. There are only some basic monitoring statics exposed to hypervisor such as VSZ and RSS in linux system. VSZ and RSS are coarse-grained statics which did not reflect the memory usage in a certern period. In the past, working set theory\cite{wss} has been widely used to capture applications' memory needs. Working sets is defined as the set of all pages accessed by a process over a given epoch. However, working set doesn't relate directly to the performance of an application. For example, if an application scans 100 pages sequentially. In a short period, the working set is 100 pages. But allocating 1 page or 100 pages gives the same memory miss ratio because the miss ratio is always 100\%. MRC is the alternative to working set theory. It plots the miss rate against given physical memory. MRC may differ every second reflecting the memory requirement changes of the application which gives us a hint to dynamic allocate more or reclaim spare memory in order to utilize the host machine's resources better.

MRC theroy is a general method to draw miss ratio curve of each part of the memory hierachy in computer storage including cache, memory and etc. Recently many research focus on the cache MRC construction. Centaur\cite{Koller2015Centaur} implements host-side SSD cache partition for VMs that provides both lower cache miss rate and better performance isolation and performance control for VM workloads. Like Centaur, Multi-Cache\cite{Rajasekaran2016Multi} presents multiple cache management on a set of storage devices and intelligently manages how caches are shared by competing VMs. Moirai\cite{Stefanovici2015Software} presents a tenant- and workload-aware system that allows data center providers to control their distributed caching infrastructure.
